Cartograms with Rivers

### 2023-03-23 paper/section/main.tex
draft: review 3

    $ \nodeSize \gets $ the initial size of all nodes \\
    $ \nodeSizeAvg \gets $ the average size of all nodes \\
    $ \nodeSizeMax \gets $ the maximum size of a node \\
    $ \stalemateMax \gets $ the maximum number of iterations indicating a stalemate \\

@@

        \State $ \nodeSize \gets 1 $
        \While{$ \nodeSizeAvg < \nodeSizeMax $}
        \State $ \nodeListCross \gets 1 $ \Comment{Trigger the while loop}
        \While{$ \nodeListCross > 0 $}

>>>>

    $ \nodeSize \gets $ the initial size of all nodes \\
    $ \nodeSizeAvg \gets $ the average size of all nodes \\
    $ \nodeSizeMax \gets $ the maximum size of a node \\
    $ \nodeErrDisplacement \gets $ the current displacement error \\
    $ \nodeErrDisplacementMax \gets $ the maximum displacement error allowed \\
    $ \stalemateMax \gets $ the maximum number of iterations indicating a stalemate \\

@@

        \State $ \nodeSize \gets 1 $
        \While{$ \nodeSizeAvg < \nodeSizeMax $ and $ \nodeErrDisplacement < \nodeErrDisplacementMax $}
        \State $ \nodeListCross \gets 1 $ \Comment{Trigger the while loop}
        \While{$ \nodeListCross > 0 $}
